\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-28 manuscript.Rnw
Minor update to discussion adding potential extnesion to automatically create tunnel states
Minor edits to use uncertainty argument when drawing parameters for PSA rather than deprecated point_estimate and/or bootstrap

The transition model is then constructed as a function of the parameters (from the fitted Weibull models) and the input data. We must also specify the allowed transitions, the desired number of PSA samples (drawn from the multivariate normal distribution of the maximum likelihood estimate of the regression coefficients), the "clock" (recall that we used a clock reset approach when fitting the Weibull models), and the starting age of the patients. Note that the starting age of the patients is useful because it allows us to specify a maximum age for patients during the simulation, ensuring that the simulated patients do not live unrealistically long lives.

<<ictstm_transmod>>=
transmod <- create_IndivCtstmTrans(wei_fits, transmod_data,
                                   trans_mat = tmat, n = n_samples,
                                   clock = "reset",
                                   start_age = patients$age)
@

@@

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
                                 bootstrap = FALSE)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@

@@

A number of extensions of the current version of \pkg{hesim} would be helpful. First, we plan to extend the individual-level simulation so that users can update input data during the simulation as a function of time elapsed and/or the health states transitioned to. This would allow potentially time-varying variables such as age to update each time a patient transitions to a new state. Second, we would like to add more examples to ensure that \pkg{hesim} is fit for purpose for a wide range of applications in health economics. Third, more complex models of utility \citep{kharroubi2007modelling, hernandez2013relationship} and costs \citep{nixon2005methods} could help better capture heterogeneity in preferences and spending. Finally, a larger aspiration is to provide support for parameterization via NMA, particularly for estimation of relative treatment effects in survival (e.g., for PSMs) and multi-state models. However, since existing \proglang{R} packages are lacking in this area, this could involve creation of a separate NMA package and a new dependency for \pkg{hesim}.

>>>>

The transition model is then constructed as a function of the parameters (from the fitted Weibull models) and the input data. We must also specify the allowed transitions, the desired number of PSA samples, the "clock" (recall that we used a clock reset approach when fitting the Weibull models), and the starting age of the patients. Parameters for the PSA are, by default, drawn from the multivariate normal distribution of the maximum likelihood estimate of the regression coefficients, although we make this explicit with the \code{uncertainty} argument. The starting age of the patients is useful because it allows us to specify a maximum age for patients during the simulation, ensuring that the simulated patients do not live unrealistically long lives.

<<ictstm_transmod>>=
transmod <- create_IndivCtstmTrans(wei_fits, transmod_data,
                                   trans_mat = tmat, n = n_samples,
                                   uncertainty = "normal",
                                   clock = "reset",
                                   start_age = patients$age)
@

@@

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
                                 uncertainty = "normal")
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@

@@

A number of extensions of the current version of \pkg{hesim} would be helpful. First, we plan to extend the individual-level simulation so that users can update input data during the simulation as a function of time elapsed and/or the health states transitioned to. This would allow potentially time-varying variables such as age to update each time a patient transitions to a new state. Second, we would like to add more examples to ensure that \pkg{hesim} is fit for purpose for a wide range of applications in health economics. Third, more complex models of utility \citep{kharroubi2007modelling, hernandez2013relationship} and costs \citep{nixon2005methods} could help better capture heterogeneity in preferences and spending. Fourth, it would be useful to add functionality that automatically creates tunnel states for users in cDTSTMs. Finally, a larger aspiration is to provide support for parameterization via NMA, particularly for estimation of relative treatment effects in survival (e.g., for PSMs) and multi-state models. However, since existing \proglang{R} packages are lacking in this area, this could involve creation of a separate NMA package and a new dependency for \pkg{hesim}.
